---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

[TEXT IN SQUARE BRACKETS IS HERE FOR GUIDANCE. PLEASE DELETE TEXT IN SQUARE BRACKETS BEFORE KNITTING THE FINAL REPORT]

# Report Details

[PILOT/COPILOT ENTER RELEVANT REPORT DETAILS HERE]

```{r}
articleID <- 2-10-2014 # insert the article ID code here e.g., "10-3-2015"
reportType <- pilot # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- Maggie Perry # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- Rondeline Williams # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- NA # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- 11/5/19 # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

Study 1's key outcomes are the differences in participants' ratings of expected curiosity and interest in their "time capsule" items at Time 1 and their actual curiousity and interest at Time 2. Measures of predicted/actual curiosity and interest (a composite measure of surprise, meaningfulness, and interest) in viewing 9 time capsule items are taken at each time point respectively. T-tests are used to measure differences in mean curiosity and interest ratings (collapsed across the 9 items) across the two time points, and Time 1 means are subtracted from Time 2 means to capture participants' underestimate.

------

#### Target outcomes: 

Table 1 provides descriptive statistics for each measure for Study 1.
Participants’ Time 1 predictions of their curiosity (M = 3.99, SD = 1.32) were lower than their actual curiosity ratings at Time 2, immediately before reading their responses (M = 4.34, SD = 1.25), t(105) = 2.88, p = .005, d = 0.27. Participants also underestimated how interesting they would find their responses. Predictions of interest at Time 1 (M = 3.54, SD = 1.01) were lower than ratings of actual interest experienced at Time 2 (M = 3.82, SD = 0.89), t(105) = 3.10, p = .003, d = 0.29.  

------

[PILOT/COPILOT DO NOT CHANGE THE CODE IN THE CHUNK BELOW]  

```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object

[PILOT/COPILOT Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
```

[PILOT/COPILOT DO NOT MAKE CHANGES TO THE CODE CHUNK BELOW]

```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
data <- read_sav("GroupC_2-10-2014/data/Study1_Data.sav")
head(data)
colnames(data)
View(data) #135 rows matches 135 participants reported before exclusions
```

# Step 3: Tidy data

```{r}
data <- data %>%
  filter(!is.na(Order)) #removed those who didn't return for T2 - matches 106 participants reported after exclusion

```

# Step 4: Run analysis

## Pre-processing

```{r}
```

## Descriptive statistics

```{r}
#Table 1 provides descriptive statistics for each measure for Study 1.

#T1 Means
#Curiosity T1 mean = 3.99
mean(data$T1_Curious, na.rm = TRUE)

#Interest Composite T1 mean = 3.54
mean(data$T1_Interest_Composite, na.rm = TRUE)

#Surprise T1 mean = 2.84
mean(data$T1_Surprised, na.rm = TRUE)

#Meaningfulness T1 mean = 3.81
mean(data$T1_Meaningful, na.rm = TRUE)

#Interesting T1 mean = 3.95
mean(data$T1_Interesting, na.rm = TRUE)


#T2 Means
#Curiosity T2 mean = 4.34
mean(data$T2_Curious, na.rm = TRUE)

#Interest Composite T2 mean = 3.82
mean(data$T2_Interest_Composite, na.rm = TRUE)

#Surprise T2 mean = 3.25
mean(data$T2_Surprised, na.rm = TRUE)

#Meaningfulness T2 mean = 4.04
mean(data$T2_Meaningful, na.rm = TRUE)

#Interesting T2 mean = 4.19
mean(data$T2_Interesting, na.rm = TRUE)


#Underestimates
#Curiosity underestimate = 0.35
mean(data$T2_Curious, na.rm = TRUE) - mean(data$T1_Curious, na.rm = TRUE)

#Interest Composite underestimate = 0.29
mean(data$T2_Interest_Composite, na.rm = TRUE) - mean(data$T1_Interest_Composite, na.rm = TRUE)

#Surprise underestimate = 0.40
mean(data$T2_Surprised, na.rm = TRUE) - mean(data$T1_Surprised, na.rm = TRUE)

#Meaningfulness underestimate = 0.22
mean(data$T2_Meaningful, na.rm = TRUE) - mean(data$T1_Meaningful, na.rm = TRUE)

#Interesting underestimate = 0.23
mean(data$T2_Interesting, na.rm = TRUE) - mean(data$T1_Interesting, na.rm = TRUE)
```

## Inferential statistics

```{r}


```

# Step 5: Conclusion

[Please include a text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]


[PILOT/COPILOT DOD NOT EDIT THE CODE CHUNK BELOW]

```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
