---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

# Report Details


```{r}
articleID <- 2-10-2014 # insert the article ID code here e.g., "10-3-2015"
reportType <- pilot # specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- Maggie Perry # insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- Rondeline Williams # # insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- 400 # insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA # insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- 11/5/19 # insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA # insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- NA # insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

Study 1's key outcomes are the differences in participants' ratings of expected curiosity and interest in their "time capsule" items at Time 1 and their actual curiousity and interest at Time 2. Measures of predicted/actual curiosity and interest (a composite measure of surprise, meaningfulness, and interest) in viewing 9 time capsule items are taken at each time point respectively. T-tests are used to measure differences in mean curiosity and interest ratings (collapsed across the 9 items) across the two time points, and Time 1 means are subtracted from Time 2 means to capture participants' underestimate.

------

#### Target outcomes: 

"Table 1 provides descriptive statistics for each measure for Study 1.
Participants’ Time 1 predictions of their curiosity (M = 3.99, SD = 1.32) were lower than their actual curiosity ratings at Time 2, immediately before reading their responses (M = 4.34, SD = 1.25), t(105) = 2.88, p = .005, d = 0.27. Participants also underestimated how interesting they would find their responses. Predictions of interest at Time 1 (M = 3.54, SD = 1.01) were lower than ratings of actual interest experienced at Time 2 (M = 3.82, SD = 0.89), t(105) = 3.10, p = .003, d = 0.29.""  

------


```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object


```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(lsr) # calculating cohen's d
library(rcompanion) #calculating confidence intervals
library(ltm) #calculating cronbach's alpha
```


```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r}
data <- read_sav("GroupC_2-10-2014/data/Study1_Data.sav")
View(data) #135 rows matches 135 participants reported before exclusions
```

# Step 3: Tidy data

```{r}
data <- data %>%
  filter(!is.na(Order)) #removed those who didn't return for T2 - matches 106 participants reported after exclusion

```

# Step 4: Run analysis

## Pre-processing

```{r}
#"Across the nine prompts, participants’ ratings of their curiosity and interest were highly intercorrelated (αcuriosity = .93, αinterest = .90)."

#Curiosity alpha = 0.93
curious.items <- dplyr::select(data, T1_Roommate_Curious, T1_Social_Curious, T1_Essay_Curious, T1_Convo_Curious, T1_Song_Curious, T1_Finals_Curious, T1_Joke_Curious, T1_Photo_Curious, T1_FB_Curious, T2_Roommate_curious, T2_Social_curious, T2_Essay_curious, T2_Convo_curious, T2_Song_curious, T2_Finals_curious, T2_Joke_curious, T2_Photo_curious, T2_FB_curious)
curious.alpha <- cronbach.alpha(curious.items, na.rm = TRUE)

#Interesting Composite alpha = 0.90
interestcomp.items <- dplyr::select(data, T1_Roommate_Interest_composite, T1_Social_Interest_composite, T1_Essay_Interest_composite, T1_Convo_Interest_composite, T1_Song_Interest_composite, T1_Finals_Interest_composite, T1_Joke_Interest_composite, T1_Photo_Interest_composite, T1_FB_Interest_composite, T2_Roommate_Interest_composite, T2_Social_Interest_composite, T2_Essay_Interest_composite, T2_Convo_Interest_composite, T2_Song_Interest_composite, T2_Finals_Interest_composite, T2_Joke_Interest_composite, T2_Photo_Interest_composite, T2_FB_Interest_composite)
interestcomp.alpha <- cronbach.alpha(interestcomp.items, na.rm = TRUE)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '.93', obtainedValue = curious.alpha, valueType = 'other') #minor error
reportObject <- reproCheck(reportedValue = '.90', obtainedValue = interestcomp.alpha, valueType = 'other')

```

## Descriptive statistics

```{r}

#"Table 1 provides descriptive statistics for each measure for Study 1."

#T1 Means (& Standard deviations for Curiosity & Interest Composite)

#Curiosity T1 mean = 3.99 [3.74, 4.24], SD = 1.32
T1.curious <- groupwiseMean(T1_Curious ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)
T1sd.curious <- sd(data$T1_Curious, na.rm = TRUE)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.99', obtainedValue = T1.curious$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.74', obtainedValue = T1.curious$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.24', obtainedValue = T1.curious$Trad.upper, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '1.32', obtainedValue = T1sd.curious, valueType = 'sd')


#Interest Composite T1 mean = 3.54 [3.34, 3.73], SD = 1.01
T1.interestcomp <- groupwiseMean(T1_Interest_Composite ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)
T1sd.interestcomp <- sd(data$T1_Interest_Composite, na.rm = TRUE)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.54', obtainedValue = T1.interestcomp$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.34', obtainedValue = T1.interestcomp$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '3.73', obtainedValue = T1.interestcomp$Trad.upper, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '1.01', obtainedValue = T1sd.interestcomp, valueType = 'sd')


#Surprise T1 mean = 2.84 [2.64, 3.05]
T1.surprise <- groupwiseMean(T1_Surprised ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '2.84', obtainedValue = T1.surprise$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '2.64', obtainedValue = T1.surprise$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '3.05', obtainedValue = T1.surprise$Trad.upper, valueType = 'ci')


#Meaningfulness T1 mean = 3.81 [3.60, 4.03]
T1.meaningful <- groupwiseMean(T1_Meaningful ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.81', obtainedValue = T1.meaningful$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.60', obtainedValue = T1.meaningful$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.03', obtainedValue = T1.meaningful$Trad.upper, valueType = 'ci')


#Interesting T1 mean = 3.95 [3.73, 4.18]
T1.interest <- groupwiseMean(T1_Interesting ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.95', obtainedValue = T1.interest$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.73', obtainedValue = T1.interest$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.18', obtainedValue = T1.interest$Trad.upper, valueType = 'ci')


#T2 Means (&Standard deviations for Curiosity & Interest Composite)
#Curiosity T2 mean = 4.34 [4.10, 4.58], SD = 1.25
T2.curious <- groupwiseMean(T2_Curious ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)
T2sd.curious <- sd(data$T2_Curious, na.rm = TRUE)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '4.34', obtainedValue = T2.curious$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '4.10', obtainedValue = T2.curious$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.58', obtainedValue = T2.curious$Trad.upper, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '1.25', obtainedValue = T2sd.curious, valueType = 'sd')


#Interest Composite T2 mean = 3.82 [3.65, 4.00], SD = 0.89
T2.interestcomp <- groupwiseMean(T2_Interest_Composite ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)
T2sd.interestcomp <- sd(data$T2_Interest_Composite, na.rm = TRUE)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.82', obtainedValue = T2.interestcomp$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.65', obtainedValue = T2.interestcomp$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.00', obtainedValue = T2.interestcomp$Trad.upper, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.89', obtainedValue = T2sd.interestcomp, valueType = 'sd')


#Surprise T2 mean = 3.25 [3.06, 3.44]
T2.surprise <- groupwiseMean(T2_Surprised ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.25', obtainedValue = T2.surprise$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.06', obtainedValue = T2.surprise$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '3.44', obtainedValue = T2.surprise$Trad.upper, valueType = 'ci')


#Meaningfulness T2 mean = 4.04 [3.84, 4.23]
T2.meaningful <- groupwiseMean(T2_Meaningful ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '4.04', obtainedValue = T2.meaningful$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '3.84', obtainedValue = T2.meaningful$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.23', obtainedValue = T2.meaningful$Trad.upper, valueType = 'ci')


#Interesting T2 mean = 4.19 [4.00, 4.38]
T2.interest <- groupwiseMean(T2_Interesting ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 3)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '4.19', obtainedValue = T2.interest$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '4.00', obtainedValue = T2.interest$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '4.38', obtainedValue = T2.interest$Trad.upper, valueType = 'ci')


#Underestimates
#Curiosity underestimate = 0.35 [0.11, 0.59]
dif.curious <- groupwiseMean(Curious_diff ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 2)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '0.35', obtainedValue = dif.curious$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '0.11', obtainedValue = dif.curious$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.59', obtainedValue = dif.curious$Trad.upper, valueType = 'ci')


#Interest Composite underestimate = 0.29 [0.10, 0.47]
dif.interestcomp <- groupwiseMean(Interest_composite_diff ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 2)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '0.29', obtainedValue = dif.interestcomp$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '0.10', obtainedValue = dif.interestcomp$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.47', obtainedValue = dif.interestcomp$Trad.upper, valueType = 'ci')


#Surprise underestimate = 0.40 [0.19, 0.62]
data$Surprised_diff <- data$T2_Surprised - data$T1_Surprised
dif.surprise <- groupwiseMean(Surprised_diff ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 2)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '0.40', obtainedValue = dif.surprise$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '0.19', obtainedValue = dif.surprise$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.62', obtainedValue = dif.surprise$Trad.upper, valueType = 'ci')


#Meaningfulness underestimate = 0.22 [0.03, 0.42]
data$Meaningful_diff <- data$T2_Meaningful - data$T1_Meaningful
dif.meaningful <- groupwiseMean(Meaningful_diff ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 2)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '0.22', obtainedValue = dif.meaningful$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '0.03', obtainedValue = dif.meaningful$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.42', obtainedValue = dif.meaningful$Trad.upper, valueType = 'ci')


#Interesting underestimate = 0.23 [0.02, 0.45]
data$Interesting_diff <- data$T2_Interesting - data$T1_Interesting
dif.interest <- groupwiseMean(Interesting_diff ~ 1, 
              data   = data, 
              conf   = 0.95, 
              digits = 2)

#Value Comparisons
reportObject <- reproCheck(reportedValue = '0.23', obtainedValue = dif.interest$Mean, valueType = 'mean')
reportObject <- reproCheck(reportedValue = '0.02', obtainedValue = dif.interest$Trad.lower, valueType = 'ci')
reportObject <- reproCheck(reportedValue = '0.45', obtainedValue = dif.interest$Trad.upper, valueType = 'ci')


#Create vectors for columns (variable, T1 mean/CI, T2 mean/CI, Underestimate)
Measure <- c("curiosity", "interestcomp", "surpise", "meaningful", "interest")

T1Mean <- c(T1.curious$Mean, T1.interestcomp$Mean, T1.surprise$Mean, T1.meaningful$Mean, T1.interest$Mean)

T1LowerCI <- c(T1.curious$Trad.lower, T1.interestcomp$Trad.lower, T1.surprise$Trad.lower, T1.meaningful$Trad.lower, T1.interest$Trad.lower)

T1UpperCI <- c(T1.curious$Trad.upper, T1.interestcomp$Trad.upper, T1.surprise$Trad.upper, T1.meaningful$Trad.upper, T1.interest$Trad.upper)

T2Mean <- c(T2.curious$Mean, T2.interestcomp$Mean, T2.surprise$Mean, T2.meaningful$Mean, T2.interest$Mean)

T2LowerCI <- c(T2.curious$Trad.lower, T2.interestcomp$Trad.lower, T2.surprise$Trad.lower, T2.meaningful$Trad.lower, T2.interest$Trad.lower)

T2UpperCI <- c(T2.curious$Trad.upper, T2.interestcomp$Trad.upper, T2.surprise$Trad.upper, T2.meaningful$Trad.upper, T2.interest$Trad.upper)

Underestimate <- round(c(dif.curious$Mean, dif.interestcomp$Mean, dif.surprise$Mean, dif.meaningful$Mean, dif.interest$Mean), digits = 2)

UndLowerCI <- c(dif.curious$Trad.lower, dif.interestcomp$Trad.lower, dif.surprise$Trad.lower, dif.meaningful$Trad.lower, dif.interest$Trad.lower)

UndUpperCI <- c(dif.curious$Trad.upper, dif.interestcomp$Trad.upper, dif.surprise$Trad.upper, dif.meaningful$Trad.upper, dif.interest$Trad.upper)

```

## Inferential statistics

```{r}

#">Participants’ Time 1 predictions of their curiosity (M = 3.99, SD = 1.32) were lower than their actual curiosity ratings at Time 2, immediately before reading their responses (M = 4.34, SD = 1.25), t(105) = 2.88, p = .005, d = 0.27."

#T test - Curious
t.curious <- t.test(data$T2_Curious, data$T1_Curious, paired = TRUE)

#Cohen's d = 0.28 ******* reported value is 0.27 - is this a rounding error?
d.curious <- cohensD(data$T1_Curious, data$T2_Curious, method = "paired")

#Value Comparisons
reportObject <- reproCheck(reportedValue = '2.88', obtainedValue = t.curious$statistic, valueType = 't')
reportObject <- reproCheck(reportedValue = '0.005', obtainedValue = t.curious$p.value, valueType = 'p')
reportObject <- reproCheck(reportedValue = '0.27', obtainedValue = d.curious, valueType = 'd') #minor error


#">Participants also underestimated how interesting they would find their responses. Predictions of interest at Time 1 (M = 3.54, SD = 1.01) were lower than ratings of actual interest experienced at Time 2 (M = 3.82, SD = 0.89), t(105) = 3.10, p = .003, d = 0.29."

#T test - Interesting Composite
t.interestcomp <- t.test(data$T2_Interest_Composite, data$T1_Interest_Composite, paired = TRUE)

#Cohen's d = 0.30 ******* off slightly again - probably not rounding error this time?
d.interestcomp <- cohensD(data$T1_Interest_Composite, data$T2_Interest_Composite, method = "paired")

#Value Comparisons
reportObject <- reproCheck(reportedValue = '3.10', obtainedValue = t.interestcomp$statistic, valueType = 't')
reportObject <- reproCheck(reportedValue = '0.003', obtainedValue = t.interestcomp$p.value, valueType = 'p')
reportObject <- reproCheck(reportedValue = '0.29', obtainedValue = d.interestcomp, valueType = 'd') #minor error


#T test - Surprise p = 0.0004
t.surprise <- t.test(data$T2_Surprised, data$T1_Surprised, paired = TRUE)

#Value Comparison
reportObject <- reproCheck(reportedValue = '<.001', obtainedValue = t.surprise$p.value, valueType = 'p', eyeballCheck = TRUE)


#T test - Meaningful p = 0.02
t.meaningful <- t.test(data$T2_Meaningful, data$T1_Meaningful, paired = TRUE)

#Value Comparison
reportObject <- reproCheck(reportedValue = '.02', obtainedValue = t.meaningful$p.value, valueType = 'p')


#T test - Interesting p = 0.03
t.interest <- t.test(data$T2_Interesting, data$T1_Interesting, paired = TRUE)

#Value Comparison
reportObject <- reproCheck(reportedValue = '.03', obtainedValue = t.interest$p.value, valueType = 'p')


#Create vector for p values
p <- round(c(t.curious$p.value, t.interestcomp$p.value, t.surprise$p.value, t.meaningful$p.value, t.interest$p.value), digits = 3)


#Create table
table <- kable(cbind(Measure, T1Mean, T1LowerCI, T1UpperCI, T2Mean, T2LowerCI, T2UpperCI, Underestimate, UndLowerCI, UndUpperCI, p))
table
```

# Step 5: Conclusion

The original study reported mean ratings of participants' curiosity, interest, surprise, and meaningfulness (and created a composite for interest) at two different time points. They then calculated the difference in those means for a "underestimate" rating. They then ran t-tests and reported the results of these for curiosity and interest composite, as well as reporting p values for all variables. I was able to reproduce all of these results, but I did encounter three minor errors:
1. The authors calculated alphas to show intercorrelation between 9 items they measured DVs on, which they then collapsed. For curiosity, I obtained an alpha of .925, consistent with the reported value of .93, but this was considered a minor error in the reproCheck. 
2. For curiosity, I obtained an effect size of d = .279, which I would round to .28, but the authors reported d = .27. I suspect this is a rounding error on the authors' end.
3. I also obtained a d value slightly different than the reported one for the interest composite variable; I obtained .300, while they reported .29. This is again a minor error, although unlikely that this was a rounding error; perhaps it is a result of using different versions of R or packages.



```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
